%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
% \input{glyphtounicode}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
    urlbordercolor=black,
    pdfborderstyle={/S/U/W 1}
}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSummary}[1]{
    #1
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% \setmainfont{Arial}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Nathan Abebe} \\ \vspace{5pt}
    \small +1 (203) 994-2951 $|$ \href{mailto:nathan.abebe@yale.edu}{nathan.abebe@yale.edu} $|$ \href{https://nathanabebe.com}{nathanabebe.com} $|$ 
    \href{https://linkedin.com/in/nathan5563}{linkedin.com/in/nathan5563} $|$
    \href{https://github.com/Nathan5563}{github.com/Nathan5563}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Yale University}{New Haven, CT}
      {B.S. Computer Science, B.S. Electrical Engineering (ABET) $|$ 3.84/4.00}{May 2028}
      \resumeItemListStart
        \resumeItem{Computer Architecture, Computer Networks, Game Engines, Algorithms, Computer Systems, Data Structures }
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Computer Graphics Group (Yale University)}{Jul 2025 -- Present}
      {Performance Engineering Researcher $|$ Advisor: \href{https://www.mshah.io/}{Dr. Mike Shah}}{Part-time, New Haven, CT}
      \resumeItemListStart
        \resumeItem{Implemented multithreaded Wavefront parser with SIMD, outperforming industry-standard parser speeds by 9x.}
        \resumeItem{Delivered 500× speedup over baseline by profiling and optimizing critical code paths over semester-long sprint.}
        \resumeItem{\textbf{Publication:} Coming soon.}
      \resumeItemListEnd
    \resumeSubheading
      {Yale School of Engineering and Applied Science}{Aug 2025 -- Present}
      {Teaching Assistant $|$ Computer Systems}{Part-time, New Haven, CT}
      \resumeItemListStart
        \resumeItem{Supported 120+ undergraduate students by holding weekly office hours on systems programming fundamentals.}
      \resumeItemListEnd
    \resumeSubheading
      {Efficient Computing Lab (Yale University)}{Jun 2025 -- Aug 2025}
      {Systems Engineering Researcher $|$ Advisor: \href{www.linzhong.org}{Prof. Lin Zhong}}{Full-time, New Haven, CT}
      \resumeItemListStart
        \resumeItem{Accomplished 80\% reduction in development time by engineering a virtual file system for multi-FPGA control, validated by DECONET/HELIOS, a production-grade distributed quantum error code decoder.}
        \resumeItem{Developed distributed network for server-FPGA communication with custom UDP/TCP protocols, achieving 100\% critical packet delivery and less than 1 minute end-to-end time for remote FPGA configuration.}
      \resumeItemListEnd
    \resumeSubheading
      {Student Technology Collaborative (Yale University)}{Oct 2024 -- May 2025}
      {Hardware Specialist}{Part-time, New Haven, CT}
      \resumeItemListStart
        \resumeItem{Diagnosed and repaired 40+ Windows, MacOS, and Linux-based laptops for students on campus.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Rocket Flight Computer -- Yale Project Liquid} $|$ \emph{Rust, Real-Time Systems, Radio Comm.}}{Jul 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed time-division multiplexed radio protocol with CRCs \& ACKs achieving sub-100ms end-to-end latency.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{\href{https://nathanabebe.com/quark}{Quark} -- 2D Game Engine} $|$ \emph{Dlang, ECS Architecture, SDL, GTK}}{Oct 2025 -- Dec 2025}
          \resumeItemListStart
            \resumeItem{Architected a 10k+ LoC parallelized 2D game engine with an entity-component system and event handlers.}
            \resumeItem{Implemented an interpreter for QScript: a specialized scripting language for use within the engine.}
            \resumeItem{Created applications on top of the engine, including a tilemap editor and various demo games.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Rocket EGSE -- Yale Project Liquid} $|$ \emph{C++, Altium Designer, LTspice, HIL Testing}}{Oct 2024 -- Dec 2025}
          \resumeItemListStart
            \resumeItem{Designed, simulated, fabricated, and tested PCBs for liquid rocket fuel control with Altium Designer and LTspice.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{\href{https://github.com/Nathan5563/ntraycer}{ntraycer} -- Path-Based Ray Tracer} $|$ \emph{Dlang, Path-Based Ray Tracing, Physics, Rendering}}{Mar 2025 -- Jul 2025}
          \resumeItemListStart
            \resumeItem{Engineered a path-based ray tracer entirely from scratch (no library imports) for generating photorealistic images.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{\href{https://github.com/Nathan5563/nnes}{nnes} -- NES Emulator} $|$ \emph{Rust, Computer Architecture, Debugging}}{Mar 2025 -- Jul 2025}
          \resumeItemListStart
            \resumeItem{Built 5K+ LoC NES emulator in Rust, down to the various graphical glitches in the NES (plays Donkey Kong!).}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{\href{https://github.com/Clash-RoYALIES/iquack_website}{TD-QAP} -- MIT iQuHack D-Wave $1^\text{st}$ Place Prize} $|$ \emph{Python, Quantum Annealing}}{Jan 2025}
          \resumeItemListStart
            \resumeItem{Solved the time-dependent quadratic assignment problem for dynamic facility layout optimization.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Rust, C, C++, Dlang, Python, Golang, x86 Assembly, TypeScript, JavaScript, C\#, SystemVerilog} \\
     \textbf{Tools \& Libraries}{: Git, GDB, Valgrind, Altium Designer, LTspice, SDL, GTK, OpenGL} \\
     \textbf{Embedded}{: STM32, RTOS, Linux, Yocto, bare-metal, PCB design, FPGA design} \\
     \textbf{Protocols}{: UDP, TCP, UART, SPI, I$^2$C, TDMA, CSMA, CRC} \\
    }}
 \end{itemize}


\end{document}----------
